---
output:
  github_document:
  html_document:
    df_print: paged
params:
  white_name: ''
---

```{r setup,include=TRUE,echo=FALSE,message=FALSE,cache=FALSE}
library(png)
library(grid)
library(readr)

# input name
white_name <- params$white_name
NameFolder <- white_name$NameFolder

# dirBackup
date <- Sys.Date()
dirAppBackup <-  "/Users/quaglieri.a/WhitePages/WhitePagesApp/backedup_files"
dirAppBackupDate <- file.path(dirAppBackup,date)
dirAppBackupImages <- file.path(dirAppBackupDate,"images")
```

## `r white_name$NameDisplay`

```{r white_name$NameFolder,echo=FALSE,warning=FALSE,fig.width=4,fig.height=3,fig.align="left"}
file_png <- list.files(file.path(dirAppBackupImages,NameFolder),full.names = TRUE)
img <- try(readPNG(file_png),silent = TRUE)

if(class(img) == "array"){
grid.raster(img)}
```


### Contact details

- **Lab**: `r ifelse(is.na(white_name$lab),"Not available",as.character(white_name$lab))`
- **Division**: `r ifelse(is.na(white_name$division),"Not available",as.character(white_name$division))`
- **Contact email**: `r ifelse(is.na(white_name$contact_email),"Not available",as.character(white_name$contact_email))`

### Equipment experience

`r ifelse(is.na(white_name$areas_of_interest_or_exper),"Not available",as.character(white_name$areas_of_interest_or_exper))`

### Lab skills

`r ifelse(is.na(white_name$lab_skills),"Not available",as.character(white_name$lab_skills))`

### Equipment experience

`r ifelse(is.na(white_name$equipment_experience),"Not available",as.character(white_name$equipment_experience))`

### Software experience

`r ifelse(is.na(white_name$software_experience),"Not available",as.character(white_name$software_experience))`

### Professional development

`r ifelse(is.na(white_name$prof_development),"Not available",as.character(white_name$prof_development))`

### Hobbies/Interests

`r ifelse(is.na(white_name$hobbies_interests),"Not available",as.character(white_name$hobbies_interests))`
