---
output:
  github_document:
  html_document:
    df_print: paged
params:
  name: ''
---

```{r setup,include=TRUE,echo=FALSE,message=FALSE,cache=FALSE}
# output: github_document

# title: "`r params$name`"
library(png)
library(grid)
library(readr)

# input name
name <- params$name
namePhotoDir <- gsub(" ","_",name)
dirApp <- "/Users/quaglieri.a/WhitePages/WhitePagesApp"
date <- Sys.Date()
backup_dir <- file.path(dirApp,"backedup_files",date)

# deatails
white_pages <- read.csv(file.path(dirApp,"data","WhitePagesData.csv"))
white_pages$Name <- paste(white_pages$first_name,white_pages$last_name)
white_name <- subset(white_pages,Name %in% name)
```

## `r name`

```{r echo=FALSE,warning=FALSE,fig.width=4,fig.height=3,fig.align="left"}
file_png <- list.files(file.path(backup_dir,"images",namePhotoDir),full.names = TRUE)
img <- try(readPNG(file_png),silent = TRUE)

if(class(img) == "array"){
grid.raster(img)}
```


### Contact details

- **Lab**: `r ifelse(is.na(white_name$lab),"Not available",as.character(white_name$lab))`
- **Division**: `r ifelse(is.na(white_name$division),"Not available",as.character(white_name$division))`
- **Contact email**: `r ifelse(is.na(white_name$contact_email),"Not available",as.character(white_name$contact_email))`

### Equipment experience

`r ifelse(is.na(white_name$areas_of_interest_or_exper),"Not available",as.character(white_name$areas_of_interest_or_exper))`

### Lab skills

`r ifelse(is.na(white_name$lab_skills),"Not available",as.character(white_name$lab_skills))`

### Equipment experience

`r ifelse(is.na(white_name$equipment_experience),"Not available",as.character(white_name$equipment_experience))`

### Software experience

`r ifelse(is.na(white_name$software_experience),"Not available",as.character(white_name$software_experience))`

### Professional development

`r ifelse(is.na(white_name$prof_development),"Not available",as.character(white_name$prof_development))`

### Hobbies/Interests

`r ifelse(is.na(white_name$hobbies_interests),"Not available",as.character(white_name$hobbies_interests))`
