---
title: "Download and backup data"
author: "Anna Quaglieri"
output:
  html_notebook:
    number_sections: yes
    toc: yes
    toc_float: yes
    fig_caption: yes
---

`r Sys.Date()`.

```{r include=FALSE,message=FALSE,echo=TRUE}
knitr::opts_chunk$set(echo = TRUE,tidy = TRUE)

library(DT)
library(tidyverse)
library(redcapAPI)
library(reshape2)
library(knitr)
library(chron)

# Directories
# Dir of the App
dirApp <- "/Users/quaglieri.a/WhitePages/WhitePagesApp"
dirRfunctions <- "/Users/quaglieri.a/WhitePages/WhitePagesApp/Rfunction"

# create backup folder with a specific date
date <- Sys.Date()
dirAppBackup <-  "/Users/quaglieri.a/WhitePages/WhitePagesApp/backedup_files"
dirAppBackupDate <- file.path(dirApp,"backedup_files",date)
dir.create(dirAppBackupDate,showWarnings = FALSE,recursive = TRUE)

# Students' photos directory
dirAppBackupImages <- file.path(dirAppBackupDate,"images")
dir.create(dirAppBackupImages,showWarnings = FALSE,recursive = TRUE)
```

# Dowload from API

```{r download_data}
api_token <- '9938D7E7B9B2D861EE7E1F4FFB64637A'
rcon <- redcapConnection(url="https://redcap.wehi.edu.au/api/", token=api_token)
white_pages <- exportRecords(rcon)
white_pages$PhotoName <- NA
```

# Clean text data

Try to mkae every text column as a list of item separated by a comma.

```{r clean_data}
# areas_of_interest_or_exper
white_pages$areas_of_interest_or_exper <- gsub("\n",",",white_pages$areas_of_interest_or_exper)
white_pages$areas_of_interest_or_exper <- gsub(" ,",",",white_pages$areas_of_interest_or_exper)
white_pages$areas_of_interest_or_exper <- gsub(",",", ",white_pages$areas_of_interest_or_exper)
white_pages$areas_of_interest_or_exper <- gsub("  "," ",white_pages$areas_of_interest_or_exper)
white_pages$areas_of_interest_or_exper <- gsub(", ,",",",white_pages$areas_of_interest_or_exper)

# equipment_experience
white_pages$equipment_experience <- gsub("\n",",",white_pages$equipment_experience)
white_pages$equipment_experience <- gsub(" ,",",",white_pages$equipment_experience)
white_pages$equipment_experience <- gsub(",",", ",white_pages$equipment_experience)
white_pages$equipment_experience <- gsub("  "," ",white_pages$equipment_experience)
white_pages$equipment_experience <- gsub(", ,",",",white_pages$equipment_experience)

# lab skills
white_pages$lab_skills <- gsub("\n",",",white_pages$lab_skills)
white_pages$lab_skills <- gsub(" ,",",",white_pages$lab_skills)
white_pages$lab_skills <- gsub(",",", ",white_pages$lab_skills)
white_pages$lab_skills <- gsub("  "," ",white_pages$lab_skills)
white_pages$lab_skills <- gsub(", ,",",",white_pages$lab_skills)

# Hobby interest
white_pages$hobbies_interests <- gsub("\n",",",white_pages$hobbies_interests)
white_pages$hobbies_interests <- gsub(" ,",",",white_pages$hobbies_interests)
white_pages$hobbies_interests <- gsub(",",", ",white_pages$hobbies_interests)
white_pages$hobbies_interests <- gsub("  "," ",white_pages$hobbies_interests)
white_pages$hobbies_interests <- gsub(", ,",",",white_pages$hobbies_interests)

# software_experience
white_pages$software_experience <- gsub("\n",",",white_pages$software_experience)
white_pages$software_experience <- gsub(" ,",",",white_pages$software_experience)
white_pages$software_experience <- gsub(",",", ",white_pages$software_experience)
white_pages$software_experience <- gsub("  "," ",white_pages$software_experience)
white_pages$software_experience <- gsub(", ,",",",white_pages$software_experience)
```

# Remove duplicated entries for students

```{r}
# Name for folder with _ between Name and Surname
# Name for display
white_pages$NameFolder <- paste(white_pages$first_name,white_pages$last_name,sep="_")
white_pages$NameDisplay <- paste(white_pages$first_name,white_pages$last_name)

# Convert wehi_white_pages_timestamp into date and time
white_pages$dtimes <- white_pages$wehi_white_pages_timestamp
dtparts = t(as.data.frame(strsplit(as.character(white_pages$dtimes),' ')))
row.names(dtparts) = NULL
thetimes = chron(dates=dtparts[,1],times=dtparts[,2],
                  format=c('y-m-d','h:m:s'))
white_pages$thetimes <- thetimes
```

## Entries with timestamp NA are removed

```{r}
white_pages[is.na(white_pages$wehi_white_pages_timestamp),]
```

- Keep only one record for student (the latest one)

```{r}
white_pages_onentry <- white_pages %>% dplyr::group_by(NameFolder) %>%
  filter(thetimes == max(thetimes))
white_pages <- white_pages_onentry

table(white_pages$NameDisplay)
table(white_pages$NameDisplay)[table(white_pages$NameDisplay) >1]
```

## Entries with Name or Surname NA are removed

```{r}
# subjects to be removed
nrow(subset(white_pages,is.na(first_name) | is.na(last_name)))

white_pages <- subset(white_pages,!is.na(white_pages$first_name) | !is.na(white_pages$last_name))
```

# Export students photos
 
```{r export_photo}
filesToExport <- melt(white_pages[, c("record_id", "first_name","last_name","photo_upload")], c("record_id","first_name","last_name"),na.rm=TRUE)

for(i in 1:nrow(filesToExport)){
  
  name_surname <- paste(filesToExport$first_name[i],filesToExport$last_name[i],sep="_")

  # create a single directory for every student
  dir.create(file.path(dirAppBackupImages,name_surname),
             showWarnings = FALSE,recursive = TRUE)

  exportFiles(rcon,  
              record=as.numeric(filesToExport$record_id[i]),
              field=as.character(filesToExport$variable[i]),
              dir = file.path(dirAppBackupImages,name_surname))
  
  PhotoName <- list.files(file.path(dirAppBackupImages,name_surname),full.names = TRUE)
  white_pages$PhotoName[white_pages$record_id == filesToExport$record_id[i]] <- as.character(PhotoName)
}
```

# Create students profiles in the same folder as the student photo

```{r include=FALSE}
for(i in 1:nrow(white_pages)){

  name_surname <- as.character(white_pages$NameFolder[i])
  print(name_surname)
  dir.create(file.path(dirAppBackupImages,name_surname),
             recursive = TRUE,showWarnings = FALSE)
  
  # Create Student profile with people's page generator
  rmarkdown::render(input=file.path(dirRfunctions,"people_page_generator.Rmd"),
          output_file  = file.path(dirAppBackupImages,name_surname,"student_profile.md"),
          params = list(white_name = white_pages[white_pages$NameFolder %in% name_surname,]))
}
```


```{r save_and_copy_to_main}
# Save data
write.csv(white_pages,file.path(dirAppBackupDate,"WhitePagesData.csv"),row.names = FALSE)

# Move data to main App folder
dirAppData <- "/Users/quaglieri.a/WhitePages/WhitePagesApp/data"
from <- file.path(file.path(dirAppBackupDate,"WhitePagesData.csv"))
to <- file.path(dirAppData,"WhitePagesData.csv")
file.copy(from,to,overwrite = TRUE)

# Move photos to main App folder
dirAppImages <-  "/Users/quaglieri.a/WhitePages/WhitePagesApp/images"
from <- file.path(file.path(dirAppBackupDate,"images"))
to <- file.path(dirApp)
file.copy(from,to,recursive = TRUE,overwrite = TRUE)

```

# Data Stats

In the backedup **White Pages** on the `r Sys.Date()` there are `r nrow(white_pages)` entries and `r ncol(white_pages)` columns.

The full **White Pages** is printed below.

```{r}
kable(white_pages)
```

- List of people present in the student's folder


```{r}
list.files(dirAppBackupImages,recursive = TRUE)
```

